---
title: "W. Jake Thompson's CV"
author: W. Jake Thompson
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "asis", 
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(tidyverse)
library(readxl)
library(magick)
library(glue)

source("parse-citations.R")
```

# Aside

```{r logo, warning = FALSE, message = FALSE, error = FALSE, out.width="100%"}
logo <- image_read("https://github.com/wjakethompson/wjakethompson.com/raw/main/static/img/logo/wjakethompson.png")
ht <- image_info(logo) %>% pull(height)
wd <- image_info(logo) %>% pull(width)
scale <- 2

image_blank(width = wd * scale, height = ht, "hotpink") %>%
  image_composite(logo, offset = paste0("+", ((wd * scale) - wd) / 2, "+0")) %>%
  image_transparent("hotpink", fuzz = 15)
```

## Contact {#contact}

-   <i class="fa fa-envelope"></i> [wjakethompson\@gmail.com](mailto:wjakethompson@gmail.com){.email}
-   <i class="fa fa-link"></i> [wjakethompson.com](https://wjakethompson.com)
-   <i class="fa fa-github"></i> [\@wjakethompson](https://github.com/wjakethompson)
-   <i class="fa fa-twitter"></i> [\@wjakethompson](https://twitter.com/wjakethompson)

## Skills {#skills}

**Programming:**

-   R
-   R Markdown
-   Stan

**Psychometrics:**

-   Diagnostic Classification Models
-   Item Response Theory
-   Reliability
-   Differential Item Functioning
-   

**Data Analysis:**

-   Bayesian statistics
-   Generalized linear models
-   Multilevel models

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`

# Main

## W. Jake Thompson {#title}

### Psychometrician & R Developer

## Education {data-icon="graduation-cap" data-concise="true"}

```{r print-edu}
edu_data <- read_xlsx("cv-data.xlsx", sheet = "education")

edu_data %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = TRUE
    ) %>% 
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{institution}",
      "\n\n",
      "{loc}",
      "\n\n",
      "{timeline}", 
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
```

## Employment {data-icon="suitcase"}

```{r print-emp}
emp_data <- read_xlsx("cv-data.xlsx", sheet = "employment")

emp_data %>%
  replace_na(list(end = "present")) %>%
  # mutate_at(vars(start, end), str_replace_all, pattern = "-[0-9]*$", "") %>%
  nest(data = -c(org, institution, loc)) %>%
  mutate(print_data = map(data, function(x) {
    current <- filter(x, end == "present")
    previous <- filter(x, end != "present")
    
    prev_positions <- x %>%
      select(title:end) %>%
      separate(start, c("start_year", "start_month"), "-", convert = TRUE) %>%
      separate(end, c("end_year", "end_month"), "-", convert = TRUE,
               fill = "right") %>%
      mutate(start_month = month.name[start_month],
             end_month = map_chr(end_month, function(x) {
               if (is.na(x)) return(NA_character_)
               month.name[x]
             }),
             label = glue("{title} ({start_month} {start_year}--{end_month} {end_year})")) %>%
      pull(label) %>%
      str_replace_all("NA ", "") %>%
      as.character() %>%
      list()
    
    current %>%
      pivot_longer(contains("description"), names_to = "description_num",
                   values_to = "description") %>%
      filter(!is.na(description)) %>%
      group_by(title) %>%
      mutate(descriptions = list(description)) %>%
      ungroup() %>%
      filter(description_num == "description_1") %>%
      mutate(full_start = min(x$start)) %>%
      separate(full_start, c("start_year", "start_month"), convert = TRUE) %>%
      mutate(timeline = glue("{end} - {month.name[start_month]} {start_year}"),
             timeline = as.character(timeline),
             description_bullets = map_chr(descriptions, ~paste("-", .x, collapse = "\n")),
             prev_pos = ifelse(nrow(previous) == 0, NA_character_,
                               paste("**Position History**\n\n",
                                     map_chr(prev_positions, ~paste("-", .x, collapse = "\n"))))) %>%
      select(title, timeline, description_bullets, prev_pos)
  })) %>%
  select(-data) %>%
  unnest(cols = c(print_data)) %>%
  glue_data(
    "### {org}{ifelse(is.na(institution), '', paste(',', institution))}",
    "\n\n",
    "{title}",
    "\n\n",
    "{loc}",
    "\n\n",
    "{timeline}",
    "\n\n",
    "{description_bullets}",
    "\n\n",
    "{ifelse(is.na(prev_pos), '', prev_pos)}",
    "\n\n\n"
  )
```

## Publications {data-icon="book"}

```{r print-pub}
format_bib("bib/pubs.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors),
         year = as.integer(year),
         month = as.integer(month)) %>%
  arrange(desc(year), desc(month), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year))) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## Conference Presentations {data-icon="users"}

```{r print-conf}
format_bib("bib/conf.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors),
         year = as.integer(year),
         month = as.integer(month)) %>%
  separate(eventdate, c("year", "month", "day"), extra = "drop", convert = TRUE) %>%
  arrange(desc(year), desc(month), desc(day), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year))) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## Technical Reports {data-icon="file-alt"}

```{r print-tech}
format_bib("bib/tech.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors),
         year = as.integer(year),
         month = as.integer(month)) %>%
  arrange(desc(year), desc(month), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year))) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## R Packages {data-icon="cube"}

```{r print-rpkg}
if (!file.exists("bib/rpkg.bib")) file.create("bib/rpkg.bib")
suppressWarnings(
  knitr::write_bib(x = c("dlmr", "rstandlm", "jayhawkdown", "ratlas"),
                   file = "bib/rpkg.bib", tweak = TRUE, width = 2000)
)

format_bib("bib/rpkg.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors, last_first = FALSE),
         year = as.integer(year)) %>%
  arrange(desc(year), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year)),
         title = map_chr(title, format_pkg_title)) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## Tutorials and Workshops {data-icon="chalkboard-teacher"}

```{r print-work}
format_bib("bib/work.bib") %>%
  mutate(across(where(is.character), ~str_replace_all(.x, "\\{|\\}", "")),
         author = map_chr(author, all_authors),
         year = as.integer(year),
         month = as.integer(month)) %>%
  separate(eventdate, c("year", "month", "day"), extra = "drop", convert = TRUE) %>%
  arrange(desc(year), desc(month), desc(day), author) %>%
  group_by(year) %>%
  mutate(count = 1:n()) %>%
  ungroup() %>%
  mutate(year = case_when(count != 1 ~ "N/A", TRUE ~ as.character(year))) %>%
  glue_data(
    "### {title}",
    "\n\n",
    "{citation}",
    "\n\n",
    "N/A",
    "\n\n",
    "{year}",
    "\n\n\n"
  )
```

## Awards {data-icon="award"}

```{r print-awds}
awd_data <- read_xlsx("cv-data.xlsx", sheet = "awards")
gnt_data <- read_xlsx("cv-data.xlsx", sheet = "grants")

awards <- awd_data %>%
  filter(display) %>%
  mutate(date = case_when(is.na(end_date) ~ as.character(start_date),
                          TRUE ~ paste0(start_date, "--", end_date)),
         display_text = glue("- {award} ({date})"),
         status = "Professional Awards") %>%
  group_by(status) %>%
  summarize(bullets = paste(display_text, collapse = "\n"))

grants <- gnt_data %>%
  mutate(display_text = glue("- **{role}:** *{title}* ({start}--{end}). {sponsor}{ifelse(is.na(funding), '.', paste0('; $', prettyNum(funding, big.mark = ','), '.'))} {ifelse(is.na(pi), '', paste0('PI: ', pi, '.'))}")) %>%
  arrange(desc(start)) %>%
  group_by(status) %>%
  summarize(bullets = paste(display_text, collapse = "\n"))


bind_rows(grants, awards) %>%
  mutate(status = factor(status,
                         levels = c("Currently Funded",
                                    "Under Review",
                                    "Previously Funded",
                                    "Unfunded",
                                    "Professional Awards"),
                         labels = c("Currently Funded Grants",
                                    "Grants Under Review",
                                    "Previously Funded Grants",
                                    "Unfunded Grants",
                                    "Professional Awards"))) %>%
  arrange(status) %>%
  glue_data(
    "### {status}",
    "\n\n",
    "{bullets}",
    "\n\n",
    "N/A",
    "\n\n\n"
  )

```

## Service {data-icon="handshake"}

### Professional Affiliations

-   American Educational Research Association (2015--present)
    -   Division D: Measurement and Research Methodology
    -   SIG: Cognition and Assessment
-   American Statistical Association (2019--present)
    -   Sections: Bayesian Statistical Science, Statistical Computing, Statistics in Sports
-   National Council on Measurement in Education (2015--present)
    -   SIGIMIE: Diagnostic Measurement (2020--present)
    -   Student Representative, Diversity and Testing Committee (2015)

N/A

### Reviewer

-   Behaviormetrika (2019--present)
-   International Journal of Research in Education and Science (2019--present)
-   Journal of Open Source Software (2019--present)
-   National Council on Measurement in Education annual meeting (2019--present)
-   American Educational Research Association, Division H, Outstanding Publications (2019)

N/A
